### 2015-04-22 thesis/thesis/chap2/chap2.tex
changes

\setcounter{chapter}{1}
%*******************************START Background **********************************

\chapter{Background and Relevant Literature}\label{sec:MAS}

In this chapter, we briefly review web services, then we introduce
the concept of communities of web services, their architecture and
applications and the benefits of forming communities. Thereafter,
we discuss the cooperative game theory concepts used throughout
the proposal. Finally, we discuss relevant related work on web
service communities and games in the literature of service
oriented computing.

@@

            \begin{example}\label{ex:simplecore1}
                Consider a game $G = (N, v)$, with two players where $N = {1,2}$. Each of these players can produce 5 units of output working alone and by collaborating they can produce 20 units worth of output. Therefore we have: $v({1}) = 5, v({2}) = 5, v({1,2}) = 20$. The $core$ of the game, which is the set of all possible distribution of gain among players guaranteeing stability is: $core(N,v) = \{(x_1,x_2) \in R^2 | x_1 >= 5, x_2 >= 5, x_1 + x_2 = 20\}$, as illustrated in figure \ref{fig:coreex1}. Distributing the 20 units of income, among these two players, for all the points in the line will make outcome stable, since non of these players can gain more than 5 by working alone. However although they have same qualities, the core can suggest a stable outcode where one agent can earn three times more than the other agent: $\{5,15\}$. As mentioned in previous section, $core$ result may not be fair, the $core$ only considers stability. However, \emph{Shapley value} considers fairness. According to equation \ref{eq:shapley}, the two  workers should each share 10 units of income, since they have the same marginal contribution to all subsets of the coalition. As you can see the distribution vector of $\{10,10\}$ is also a member in $core$ set. Later we are going to show if $core$ of a coalition game is not empty, and game is convex, the shapely value lies within $core$ set.
            \end{example}

@@

        \subsection{Representation and Complexity issues}\label{sec:CWSArchitecture}

        Shapely value is the unique "fair" way to distribute the total surplus generated by the coalition, among all the players.
        The nature of the Shapley value is combinatorial, as all possible orderings to form a
        coalition needs to be considered. This computational complexity can sometimes be
        an advantage as agents cannot benefit from manipulation. For example, it is NP-complete
        to determine whether for a bunch of agents to collude and make their own coalition and guarantee
        an increase in payoff of all participants\cite{conf/aaai/YokooCSOI05}.
        There are some representations that allow to compute the Shapley value efficiently by reducing the input size of the problem.
        One example is \emph{Induced subgraph games}
        which was introduced by Deng and Papadimitriou \cite{Deng94}. In this representation, players are represented by graph nodes, and
        their valuation function should be sum of weights all edges between the node and all its neighbors. It is a succinct representation, using
        an adjacency matrix, which need only $O(n^2)$ space to store all the input, which is a big reduction from $O(2^n)$.
        if weights of all the edges in graph are all positive, the Shapley value can be computed in $O(n^2)$ time.
        However, this representation is not complete, some games cannot be represented by a induced subgraph game\cite{conf/aaai/YokooCSOI05}.

        Ketchpel introduces the Bilateral Shapley Value (BSV)\cite{conf/aaai/Ketchpel94a} for coalition games with general valaution functions.
        It reduces the combinatorial complexity of the computation of the Shapley value, breaking the community to multiple disjoint set.
        With backtracking and dynamic programming like methods, they merge and store the marginal contribution of disjoint coalitions,
        reducing the overall complexity of the algorithm. However, the solution is still NP-Complete and BSV time and space complexity grows exponentially.

@@

        In \cite{10.1109/TSC.2012.12}, a cooperative scheme among autonomous
        web services based on coalitional game theory has been introduced. They have proposed an algorithm to
        reach individually stable coalition partition for web services in order to
        maximize their efficiency. The communities choose new web services on the promise
        that it would benefit the community without decreasing any other web service's
        income. In their model, the worth of community is evaluated with high emphasis on
        availability metric and considering price and cost values only. The community structure is based on a coordination chain,
        where a web service is assigned as a \emph{primary} web service and the community task destribution
        method, will initially invoke the primary web service and only if the primary web service is unavailable
        will invoke the next backup web services as they are ordered in the coordination chain. However in cooperative models, it is preferred to
        have a real and active cooperative activity engaging all agents to perform the tasks more efficiently. Especially nowadays
        with recent advancement in cloud and hardware infrastructures availability is becoming less of an issue. So the backup web services
        in their model have a very low chance of getting jobs, especially the ones further in chain, which is huge waste of web services
        capabilities.

        In this research work, I will use game theory to
        propose a cooperative game model for the aggregation of web
        services within communities. The solution concepts of our
        cooperative game seeks to find efficient ways of forming
        coalitions (teams) of web services so that they can maximize their
        gain and payoff, and distribute the gain in a fair way among all
        the web services. Achieving Fairness when the gain is distributed
        among the community members is the main factor to keep the
        coalition stable as no web service will expect to gain better by
        deviating for the community. In other words, the coalition is made
        efficient if all the members are satisfied. We first propose a
        representation function for communities of web services based on
        their QoS attributes. By using this function, we can evaluate the
        $worth$ of each community of web services. When facing new
        membership requests, a typical community master checks whether the
        new coalition having the old and new set of web services will keep
        the community stable or not. The community master will reject the
        membership requests if it finds out that the new coalition would
        be unstable, preventing $any$ subset of web services from gaining
        significantly more by deviating from the community and joining
        other communities or forming new ones. The computation of
        solutions for cooperative game theory problems is combinatorial in
        nature and proven to be NP-complete \cite{Algorithmic}, making
        this computation impractical in real world applications. However,
        using the concepts of coalition stability, we propose
        approximation algorithms running in polynomial time providing web
        services and community masters with applicable and near-optimal
        decision making mechanisms.

%*******************************End Background **********************************

>>>>

\setcounter{chapter}{1}

\chapter{Background}\label{cha:background}
In this chapter, we briefly review web services, then we introduce
the concept of communities of web services, their architecture and
applications and the benefits of forming communities. Thereafter,
we discuss the cooperative game theory concepts used throughout
the proposal. Finally, we discuss relevant related work on web
service communities and games in the literature of service
oriented computing.

@@

\begin{example}\label{ex:simplecore1}
Consider a game $G = (N, v)$, with two players where $N = {1,2}$.
Each of these players can produce 5 units of output working alone
and by collaborating they can produce 20 units worth of output.
Therefore we have: $v({1}) = 5, v({2}) = 5, v({1,2}) = 20$. The
$core$ of the game, which is the set of all possible distribution
of gain among players guaranteeing stability is: $core(N,v) =
\{(x_1,x_2) \in R^2 | x_1 >= 5, x_2 >= 5, x_1 + x_2 = 20\}$, as
illustrated in Figure 2. Distributing the 20 units of income,
among these two players, for all the points in the line will make
outcome stable, since non of these players can gain more than 5 by
working alone. However although they have same qualities, the core
can suggest a stable outcode where one agent can earn three times
more than the other agent: $\{5,15\}$. As mentioned in previous
section, $core$ result may not be fair, the $core$ only considers
stability. However, \emph{Shapley value} considers fairness.
According to equation \ref{eq:shapley}, the two  workers should
each share 10 units of income, since they have the same marginal
contribution to all subsets of the coalition. As you can see the
distribution vector of $\{10,10\}$ is also a member in $core$ set.
Later we are going to show if $core$ of a coalition game is not
empty, and game is convex, the shapely value lies within $core$
set.
\end{example}

@@

        \subsection{Representation and Complexity Issues}\label{sec:CWSArchitecture}

        Shapely value is the unique ``fair'' way to distribute the total surplus generated by the coalition, among all the players.
        The nature of the Shapley value is combinatorial, as all possible orderings to form a
        coalition needs to be considered. This computational complexity can sometimes be
        an advantage as agents cannot benefit from manipulation. For example, it is NP-complete
        to determine whether for a bunch of agents to collude and make their own coalition and guarantee
        an increase in payoff of all participants \cite{conf/aaai/YokooCSOI05}.
        There are some representations that allow us to compute the Shapley value efficiently by reducing the input size of the problem.
        One example is \emph{Induced subgraph games}
        which was introduced by Deng and Papadimitriou \cite{Deng94}. In this representation, players are represented by graph nodes, and
        their valuation function should be the sum of weights of all edges between the node and all its neighbors. It is a succinct representation, using
        an adjacency matrix, which needs only $O(n^2)$ space to store all the input, which is a major improvement from $O(2^n)$ because
        if weights of all the edges in graph are all positive, the Shapley value can be computed in time $O(n^2)$.
        However, this representation is not complete, some games cannot be represented by a induced subgraph game \cite{conf/aaai/YokooCSOI05}.

        Ketchpel introduces the Bilateral Shapley Value (BSV) \cite{conf/aaai/Ketchpel94a} for coalition games with general valaution functions.
        It reduces the combinatorial complexity of the computation of the Shapley value, breaking the community to multiple disjoint set.
        With backtracking and dynamic programming like methods, they merge and store the marginal contribution of disjoint coalitions,
        reducing the overall complexity of the algorithm. However, the solution is still NP-Complete and BSV time and space complexity grows exponentially.

@@

        In \cite{10.1109/TSC.2012.12}, a cooperative scheme among autonomous
        web services based on coalitional game theory has been introduced. The authors have proposed an algorithm to
        reach individually stable coalition partition for web services in order to
        maximize their efficiency. The communities choose new web services on the promise
        that it would benefit the community without decreasing any other web service's
        income. In their model, the worth of community is evaluated with high emphasis on
        availability metric and considering price and cost values only. The community structure is based on a coordination chain,
        where a web service is assigned as a \emph{primary} web service and the community task destribution
        method, will initially invoke the primary web service and only if the primary web service is unavailable
        will invoke the next backup web services as they are ordered in the coordination chain. However in cooperative models, it is preferred to
        have a real and active cooperative activity engaging all agents to perform the tasks more efficiently. Especially nowadays
        with recent advancement in cloud and hardware infrastructures availability is becoming less of an issue. So the backup web services
        in their model have a very low chance of getting jobs, especially the ones further in chain, which is huge waste of web services
        capabilities.

\section{Conclusive Remarks}

        In this research work, we will use game theory to
        propose a cooperative game model for the aggregation of web
        services within communities. The solution concepts of our
        cooperative game seeks to find efficient ways of forming
        coalitions (teams) of web services so that they can maximize their
        gain and payoff, and distribute the gain in a fair way among all
        the web services. Achieving Fairness when the gain is distributed
        among the community members is the main factor to keep the
        coalition stable as no web service will expect to gain better by
        deviating from the community. In other words, the coalition is made
        efficient if all the members are satisfied. We first propose a
        representation function for communities of web services based on
        their QoS attributes. By using this function, we can evaluate the
        $worth$ of each community of web services. When facing new
        membership requests, a typical community master checks whether the
        new coalition having the old and new set of web services will keep
        the community stable or not. The community master will reject the
        membership requests if it finds out that the new coalition would
        be unstable, preventing $any$ subset of web services from gaining
        significantly more by deviating from the community and joining
        other communities or forming new ones. The computation of
        solutions for cooperative game theory problems is combinatorial in
        nature and proven to be NP-complete \cite{Algorithmic}, making
        this computation impractical in real world applications. However,
        using the concepts of coalition stability, we propose
        approximation algorithms running in polynomial time providing web
        services and community masters with applicable and near-optimal
        decision making mechanisms.
